---
title: "NYC Flights"
author: "Alex Lindquist"
date: "9/9/2022"
output: html_notebook
---

Class play with NYC flights data.

##Load Packages

```{r}
library(nycflights13)
library(tidyverse)
library(here)
library(janitor)
```

##Load Flight Data

```{r}
df1 = flights
```

##Class Work

```{r}
df2=df1 %>%
  filter(origin == "MIA", month == 9)
```

```{r}
df3=df1 %>%
  filter(dest=="MIA", month==9)
```

```{r}
df4=df1 %>%
  filter(month==1, dest=="MIA")
```

```{r}
df5=df1 %>%
  filter(month==7, dest=="MIA")
```

```{r}
df6=df1 %>%
  filter(dest=="MIA")

df6 %>% ggplot(aes(month)) + geom_bar()
```
Analyzing the graph above, we note:

* December has the most flights, perhaps due to holiday.
* Feb is low, perhaps due to fewer days in Feb.
* Flight numbers seem to correlate with days in the month.

```{r}
df7=df1 %>%
  filter(dest %in% c("LAX", "SAN", "SFO", "ATL", "ORD", "MIA"))

df7 %>% ggplot(aes(month)) + geom_bar()
```

```{r}
df7=df1 %>%
  filter(dest %in% c("LAX", "SAN", "SFO", "ATL", "ORD", "MIA"))

df7 %>% ggplot(aes(x = month, fill = dest)) + geom_bar()
```

```{r}
df7 %>% ggplot(aes(x = month, fill = dest)) + geom_bar() + facet_wrap(~dest)
```
Observation from above graph:

* San Francisco is a smaller airport than the others.
* ORD gets significantly more traffic during the summer months.
* MIA is _unusually_ flat.
* ORD, LAX, SFO patterns appear to be similar; low in winter, high in summer.
* ATL is flat, perhaps because it's a hub.
* Feb is low, because of fewer days and winter.


